Experiment 2

### 2021-06-30 experiments/experiment 1/experiment 1.Rmd
moved some functionality into functions!

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_gmax_div
CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_h_div
SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_gmax_div
SB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * SB_h_div
PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_gmax_div
PB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * PB_h_div
var_expt <- tibble(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

@@

tmp_novar <- sim_res_novar$result %>%
  filter(time != 0) %>%
  select(-time) %>%
  mutate(direction = rep(c("down", "up"), each = n()/2)) %>%
  pivot_longer(1:(num_CB_strains+num_SB_strains+num_PB_strains+4),
               names_to = "Species", values_to = "Quantity") %>%
  mutate(var_type=ifelse(grepl("B_", Species), "Organism", "Substrate"),
         functional_group = case_when(str_detect(Species, "CB_") ~ "CB",
                                      str_detect(Species, "SB_") ~ "SB",
                                      str_detect(Species, "PB_") ~ "PB"),
         functional_group = ifelse(is.na(functional_group), Species, functional_group)) %>%
  group_by(functional_group, a, var_type, direction) %>%
  summarise(Total_quantity = sum(Quantity))
tmp_highvar <- sim_res_highvar$result %>%
  filter(time != 0) %>%
  select(-time) %>%
  mutate(direction = rep(c("down", "up"), each = n()/2)) %>%
  pivot_longer(1:(num_CB_strains+num_SB_strains+num_PB_strains+4),
               names_to = "Species", values_to = "Quantity") %>%
  mutate(var_type=ifelse(grepl("B_", Species), "Organism", "Substrate"),
         functional_group = case_when(str_detect(Species, "CB_") ~ "CB",
                                      str_detect(Species, "SB_") ~ "SB",
                                      str_detect(Species, "PB_") ~ "PB"),
         functional_group = ifelse(is.na(functional_group), Species, functional_group)) %>%
  group_by(functional_group, a, var_type, direction) %>%
  summarise(Total_quantity = sum(Quantity))

soi <- "O"
ggplot() +
  geom_path(data = filter(tmp_novar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction)) +
  geom_path(data = filter(tmp_highvar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction),
            linetype = "dashed", lwd=2, col="red") +
  ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
##ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

@@

>>>>

```{r}
var_expt <- create_diversity()
```

@@

```{r}
visualise_temporal_env_eco()
```

@@

```{r}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

@@

```{r}
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))

### 2021-06-30 experiments/experiment 2/experiment 2.Rmd
moved some functionality into functions!

devtools::install_github("opetchey/microxanox",
                             ref="main",
                             auth_token = "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",
                             build_vignettes = FALSE,
                             force = TRUE)

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))

@@

>>>>

# devtools::install_github("opetchey/microxanox",
#                              ref="main",
#                              auth_token = "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",
#                              build_vignettes = FALSE,
#                              force = TRUE)

@@

```{r}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))

@@

```{r}
var_expt <- readRDS(here("experiments/experiment 2/data/ss_data.RDS"))
